---
title: "Structuring Code for Reuse"
output: html_notebook
---

# Define the sales transaction data
```{r}
sales_df <- data.frame(UnitPrice = c(87.67, 20.01, 30.14, 83.24, 98.98),
                       Quantity = c(2L, 9L, 10L, 9L, 10L),
                       COGS = c(170.12, 174.55, 284.76, 709.60, 955.90),
                       CustomerType = factor(c("N", "M", "M", "N", "N")))
sales_df
```
# Define a function to print all values from a column
```{r}
print_col_vals <- function(x) {
  for (i in x) {
    print(i)
  }
}
```
# Call the function to print all values from a column
```{r}
print_col_vals(sales_df$UnitPrice)
```
# Define a function to obtain revenue with the membership discount applied
```{r}
get_rev <- function(df, price, quant, type) {
  revenue <- 0
  
  for (i in 1:nrow(df)) {
    if (df[i, type] == "M") {
      calc_price <- df[i, price] * 0.95
    } else {
      calc_price <- df[i, price]
    }
    
    revenue[i] <- round(calc_price * df[i, quant], digits = 2)
  }
  
  return(revenue)
}
```
# Call the function to obtain revenue
```{r}
get_rev(sales_df, "UnitPrice", "Quantity", "CustomerType")
```
# Define a function to obtain gross income
```{r}
get_inc <- function(df, ..., cogs) {
  revenue <- get_rev(df, ...)
  
  income <- revenue - df[cogs]
  
  colnames(income) <- "GrossIncome"
  
  return(income)
}
```
# Call the function to obtain gross income
```{r}
get_inc(sales_df, "UnitPrice", "Quantity", "CustomerType", cogs = "COGS")
```
# Get a list of max values for each numeric variable
```{r}
lapply(sales_df[1:3], max)
```
# Get a simplified vector of max values for each numeric variable
```{r}
sapply(sales_df[1:3], max)
```
# Get the highest unit price for members and non-members
```{r}
tapply(sales_df$UnitPrice, sales_df$CustomerType, max)
```
# Get the floor of the minimum values for both monetary variables
```{r}
sapply(sales_df[c("UnitPrice", "COGS")], function(x) { floor(min(x)) })
```
# Define the customer sentiment data
```{r}
cust_df <- data.frame(ProdScores = c(5.7, 7.2, 8.9, 4.0, 6.1, 6.1),
                      ServScores = c(9.2, 4.0, 4.0, 4.5, 8.9, 5.2),
                      Return = factor(c("Yes", "No", "No",
                                        "Yes", "Yes", "Yes")))
cust_df
```
# Get the average of both scores for each customer
```{r}
apply(cust_df[1:2], 1, mean)
```
# Generate a new data frame of random product and customer service scores
```{r}
rand_scores <- mapply(runif, 5, c(1.0, 4.0), 10.0)
rand_scores <- as.data.frame(round(rand_scores, digits = 1))
colnames(rand_scores) <- colnames(cust_df[1:2])
rand_scores
```
# Identify the paths to your R library
```{r}
.libPaths()
```
# Identify the packages currently loaded in the R session
```{r}
search()
```
# Download and install the tidyverse collection
```{r}
install.packages("tidyverse")
```
# Load the dplyr package from tidyverse
```{r}
library(dplyr)
search()
```
# Use a function from the dplyr package
```{r}
filter(sales_df, Quantity == 9)
```
# Reference a function with the same name from the stats package
```{r}
?stats::filter
```