---
title: "Managing Data in R"
output: html_notebook
---

# Load the customer and store data
```{r}


```
# Load more customer and store data
```{r}




```
# Load the financial data for the transactions
```{r}


```
# Load the customer ratings data
```{r}


```
# Load the remaining data for the last six transactions
```{r}


```
# Convert categorical columns to factors
```{r}






```
# Save the converted data frame as a text file
```{r}

```
# Save the converted data frame as a binary file
```{r}

```
# Append transaction rows to an overall data frame
```{r}


```
# Add multiple columns to the new data frame
```{r}


```
# Add a single column to the new data frame
```{r}


```
# Transpose and data so it's in a more common format
```{r}


```
# Convert relevant columns to integer or numeric type
```{r}












```

# Move transposed row names into a column, then append the rows
```{r}





```
# Sort the customer ratings
```{r}


```
# Sort the entire data frame by customer rating
```{r}


```
# Load dplyr into R
```{r}

```
# Load a data file of customer return status
```{r}


```
# Perform a left outer join to merge the return status data
```{r}


```
# Verify the merge worked as expected
```{r}


```
# Rename columns related to customer details
```{r}




```
# Get all customer-based column data
```{r}

```
# Generate new columns for revenue and gross income
```{r}



```
# Retrieve all transactions where income margins are less than 2%
```{r}

```
# Identify purchases that qualify for the clothing deal
```{r}




```
# Sort the data by customer rating, gender, and membership
```{r}

```
# Get the mean customer rating for males and females
```{r}


```
# Get the highest single-transaction revenue from each branch
```{r}

```
# Create a new column to hold both the date and the time
```{r}



```
# Convert the DateTime column to the proper data type
```{r}



```
# Load the lubridate package
```{r}

```
# Get all transactions from February
```{r}

```
# Get purchases made on February 12th by gender and product line
```{r}

```
# Get the mean revenue of transactions for each day of the week
```{r}

```
# Get the mean customer age for morning shoppers vs. the rest of the day
```{r}

```