---
title: "Managing Data in R"
output: html_notebook
---

# Load the customer and store data
```{r}
cust_store_data <- read.csv("../data/cust_store_data.csv", na.strings = "")
cust_store_data
```
# Load more customer and store data
```{r}
cust_store_data_more <- read.table("../data/cust_store_data_more.txt",
                                   sep = ";", header = TRUE, na.strings = "")
cust_store_data_more
```
# Load the financial data for the transactions
```{r}
financials <- dget(file = "../data/financials.R")
financials
```
# Load the customer ratings data
```{r}
load("../data/ratings.rda")
ratings
```
# Load the remaining data for the last six transactions
```{r}
last_transactions <- readRDS("../data/remaining_data.rda")
last_transactions
```
# Convert categorical columns to factors
```{r}
categ_cols <- c("Gender", "Type", "Branch", "ProductLine")

for (col in categ_cols) {
  cust_store_data[[col]] <- factor(cust_store_data[[col]])
}
cust_store_data
```
# Save the converted data frame as a text file
```{r}
write.csv(cust_store_data, "factorized_data.csv")
```
# Save the converted data frame as a binary file
```{r}
saveRDS(cust_store_data, "factorized_data.rda")
```
# Append transaction rows to an overall data frame
```{r}
gce_trial <- rbind(cust_store_data, cust_store_data_more)
gce_trial
```
# Add multiple columns to the new data frame
```{r}
gce_trial <- cbind(gce_trial, financials[c("UnitPrice", "Quantity", "COGS")])
gce_trial
```
# Add a single column to the new data frame
```{r}
gce_trial$CustomerRating <- ratings$CustomerRating
gce_trial
```
# Transpose and data so it's in a more common format
```{r}
tposed_df <- as.data.frame(t(last_transactions))
tposed_df
```
# Convert relevant columns to integer or numeric type
```{r}
int_cols <- c("Age", "Quantity")
num_cols <- c("UnitPrice", "COGS", "CustomerRating")

for (col in int_cols) {
  tposed_df[[col]] <- as.integer(tposed_df[[col]])
}

for (col in num_cols) {
  tposed_df[[col]] <- as.numeric(tposed_df[[col]])
}

tposed_df
```

# Move transposed row names into a column, then append the rows
```{r}
new_tposed_df <- tposed_df
new_tposed_df$InvoiceID <- rownames(tposed_df)
rownames(new_tposed_df) <- NULL
gce_trial <- rbind(gce_trial, new_tposed_df)
gce_trial
```
# Sort the customer ratings
```{r}
ratings_sort <- sort(gce_trial$CustomerRating)
ratings_sort[1:50]
```
# Sort the entire data frame by customer rating
```{r}
ratings_order <- order(gce_trial$CustomerRating, decreasing = TRUE)
gce_trial[ratings_order, ]
```
# Load dplyr into R
```{r}
library(dplyr)
```
# Load a data file of customer return status
```{r}
return_status <- read.csv("../data/return_status.csv")
return_status
```
# Perform a left outer join to merge the return status data
```{r}
gce_trial <- left_join(gce_trial, return_status, by = "InvoiceID")
gce_trial
```
# Verify the merge worked as expected
```{r}
match <- filter(gce_trial, InvoiceID == "GRC-HBE-001")
select(match, c(InvoiceID, Returned))
```
# Rename columns related to customer details
```{r}
gce_trial <- rename(gce_trial, CustName = Name, CustGender = Gender,
                    CustAge = Age, CustType = Type,
                    CustRating = CustomerRating, CustReturned = Returned)
gce_trial
```
# Get all customer-based column data
```{r}
gce_trial %>% select(starts_with("Cust"))
```
# Generate new columns for revenue and gross income
```{r}
gce_trial <- gce_trial %>% mutate(Revenue = UnitPrice * Quantity)
gce_trial <- gce_trial %>% mutate(GrossIncome = Revenue - COGS)
gce_trial
```
# Retrieve all transactions where income margins are less than 2%
```{r}
gce_trial %>% filter(GrossIncome / Revenue < 0.02) %>% select(Branch, COGS, Revenue, GrossIncome)
```
# Identify purchases that qualify for the clothing deal
```{r}
gce_trial %>% filter(Branch == "Carbon Creek"
                     & CustType == "Member"
                     & ProductLine == "Clothing"
                     & UnitPrice >= 75)
```
# Sort the data by customer rating, gender, and membership
```{r}
gce_trial %>% arrange(desc(CustRating), CustGender, CustType)
```
# Get the mean customer rating for males and females
```{r}
gender_grp <- gce_trial %>% group_by(CustGender)
gender_grp %>% summarize(MeanCustRating = mean(CustRating))
```
# Get the highest single-transaction revenue from each branch
```{r}
gce_trial %>% group_by(Branch) %>% summarize(TopRevenue = max(Revenue))
```
# Create a new column to hold both the date and the time
```{r}
gce_trial <- gce_trial %>% group_by(Date, Time) %>% mutate(DateTime = paste(Date, Time)) %>% ungroup(Date, Time) %>% select(!c(Date, Time)) %>% relocate(DateTime, .after = InvoiceID)

gce_trial
```
# Convert the DateTime column to the proper data type
```{r}
dt_vals <- as.POSIXct(gce_trial$DateTime, format = "%m/%d/%Y %H:%M:%S")
gce_trial$DateTime <- dt_vals
gce_trial
```
# Load the lubridate package
```{r}
library(lubridate)
```
# Get all transactions from February
```{r}
gce_trial %>% filter(month(DateTime) == 2)
```
# Get purchases made on February 12th by gender and product line
```{r}
gce_trial %>% filter(month(DateTime) == 2 & mday(DateTime) == 12) %>% arrange(CustGender, ProductLine) %>% select(CustGender, ProductLine)
```
# Get the mean revenue of transactions for each day of the week
```{r}
gce_trial %>% group_by(wday(DateTime)) %>% summarize(MeanRev = mean(Revenue))
```
# Get the mean customer age for morning shoppers vs. the rest of the day
```{r}
gce_trial %>% mutate(AM = hour(DateTime) >= 8 & hour(DateTime) < 12) %>% group_by(AM) %>% summarize(MeanAge = mean(CustAge))
```