---
title: "Visualizing Data in R"
output: html_notebook
---

# Load the dataset and relevant packages
```{r message = FALSE}
library(dplyr)
library(lubridate)
load("../data/gce_trial.rda")
gce_trial
```
# Generate a scatter plot comparing revenue and gross income
```{r}
plot(gce_trial$Revenue, gce_trial$GrossIncome)
```
# Generate a line plot of revenue over each day in January
```{r}
jan_only <- gce_trial %>% filter(month(DateTime) == 1)
days_rev <- jan_only %>% group_by(Days = mday(DateTime)) %>% summarize(Revenue = sum(Revenue))

plot(days_rev$Days, days_rev$Revenue, type = "l")
```
# Generate a bar chart of each branch's total revenue
```{r}
branch_rev <- gce_trial %>% group_by(Branch = Branch) %>% summarize(TotalRevenue = sum(Revenue))

barplot(branch_rev$TotalRevenue, names.arg = branch_rev$Branch)
```
# Generate a histogram showing the distribution of COGS
```{r}
hist(gce_trial$COGS)
```
# Generate a box plot showing the distribution of COGS
```{r}
boxplot(gce_trial$COGS)
```
# Load the ggplot2 package
```{r}
library(ggplot2)
```
# Generate a histogram of revenue
```{r}
ggplot(gce_trial) + geom_histogram(aes(Revenue), bins = 10)
```
# Generate violin plots comparing the gross income distribution across each branch
```{r}
ggplot(gce_trial) + geom_violin(aes(Branch, GrossIncome), draw_quantiles = 0.5)
```
# Generate stack plots to compare total items sold for each day in the first three months
```{r}
jan_feb_quant <- gce_trial %>% group_by(Days = mday(DateTime), Month = month(DateTime)) %>% summarize(Quantity = sum(Quantity))
jan_feb_quant$Month <- as.factor(jan_feb_quant$Month)
levels(jan_feb_quant$Month) <- c("Jan", "Feb", "Mar")

ggplot(jan_feb_quant) + geom_area(aes(Days, Quantity, fill = Month, group = Month))
```
# Generate a scatter plot comparing quantity to revenue
```{r}
ggplot(gce_trial) + geom_point(aes(Quantity, Revenue))
```
# Generate a jitter plot comparing quantity to revenue by gender
```{r}
ggplot(gce_trial) + geom_jitter(aes(Quantity, Revenue, color = CustGender))
```
# Generate a bar chart of mean revenue for each branch for the health and beauty product line
```{r}
hlth_beaut <- gce_trial %>% filter(ProductLine == "Health and beauty")
branch_sum <- hlth_beaut %>% group_by(Branch) %>% summarize(MeanRevenue = mean(Revenue))

ggplot(branch_sum) + geom_bar(aes(Branch, MeanRevenue), stat = "identity")
```
# Create a data frame for plotting total revenue each day for January and February
```{r}
jan_feb <- gce_trial %>% filter(month(DateTime) %in% c(1, 2))
rev_sum <- jan_feb %>% group_by(Days = mday(DateTime), Month = month(DateTime)) %>% summarize(TotalRev = sum(Revenue))
rev_sum$Month <- as.factor(rev_sum$Month)

rev_sum
```
# Generate a line graph of revenue by month
```{r}
rev_gg <- ggplot(rev_sum)
rev_plt <- rev_gg + geom_line(aes(Days, TotalRev, group = Month, color = Month, linetype = Month), size = 1)

rev_plt
```
# Add a title to the plot and format it
```{r}
rev_plt <- rev_plt + ggtitle("Daily Revenue for One Month")
rev_plt <- rev_plt + theme(plot.title = element_text(family = "serif", face = "bold", color = "grey30", size = 14, hjust = 0.5))

rev_plt
```
# Modify the axis labels
```{r}
rev_plt <- rev_plt + ylab("Revenue \n(USD)") + theme(axis.title.y = element_text(face = "bold", angle = 0, vjust = 0.5, color = "grey30"))

rev_plt <- rev_plt + xlab("Day of Month") + theme(axis.title.x = element_text(face = "bold", color = "grey30"))

rev_plt
```
# Expand the y-axis upper limit
```{r}
rev_plt <- rev_plt + ylim(0, 8000)

rev_plt
```
# Add more ticks to the x-axis
```{r}
rev_plt <- rev_plt + scale_x_continuous(breaks = seq(0, 30, 5))

rev_plt
```
# Modify the legend
```{r}
rev_plt <- rev_plt + theme(legend.background = element_rect(color = "grey"), legend.key = element_rect(fill = NA), legend.title = element_text(hjust = 0.5))

rev_plt
```
# Apply a color palette to the lines and change the legend item labels
```{r}
pal <- c("#CD5C5C", "#3C7FC2", "#3C3C97", "#89BB3D")
leg_lbls <- c("January", "February") 

rev_plt <- rev_plt + scale_color_manual(values = pal, name = "Month", labels = leg_lbls)

rev_plt
```
# Change the line types
```{r}
rev_plt <- rev_plt + scale_linetype_manual(values = c("twodash", "solid"), name = "Month", labels = leg_lbls)

rev_plt
```
# Add an annotation explaining a sharp drop in revenue
```{r}
rev_plt <- rev_plt + annotate("segment", x = 9, y = 900, xend = 12.5, yend = 900, arrow = arrow(length = unit(2, "mm")))

rev_plt <- rev_plt + annotate("text", x = 7, y = 900, label = "Snowstorm", size = 2.5)

rev_plt
```
# Save the revenue line plot as a file
```{r}
ggsave("rev_jan_feb.png", width = 7.5, height = 5)
```
# Generate a bar chart that compares the quantity sold for each product line and branch
```{r}
qty_sum <- gce_trial %>% group_by(ProductLine, Branch, CustReturned) %>% summarize(Quantity = sum(Quantity))

prod_bar <- ggplot(qty_sum) +
  geom_bar(aes(ProductLine, Quantity, fill = Branch), color = "black", position = "dodge", stat = "identity") +
  ggtitle("Quantity Sold for Each Product Line") +
  theme(plot.title = element_text(face = "bold", size = 12, hjust = 0.5)) +
  theme(panel.grid.major.x = element_blank()) +
  theme(axis.text.x = element_text(face = "bold", size = 6)) +
  theme(panel.background = element_rect(fill = "#EFEFFA")) +
  xlab("Product Line") +
  scale_fill_brewer(palette = "Set2") +
  scale_y_continuous(breaks = seq(0, 400, 50)) +
  scale_x_discrete(labels = c("Clothing", "Electronics", "Food and\nbeverages", "Health and\nbeauty", "Home and\nlifestyle", "Sports and\ntravel"))

prod_bar
```
# Compare the distributions of revenue and quantity
```{r}
revenue <- gce_trial$Revenue
quantity <- gce_trial$Quantity

par(mfrow = c(1, 2))
hist(revenue, breaks = 10)
hist(quantity, breaks = 10)
```
# Compare quantity sold per product line and branch in a facet wrap
```{r}
prod_wrap <- ggplot(qty_sum) +
  geom_bar(aes(Branch, Quantity, fill = Branch), color = "black", position = "dodge", stat = "identity") + 
  facet_wrap(~ ProductLine) +
  
  # Formatting
  ggtitle("Quantity Sold for Each Product Line") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(panel.grid.major.x = element_blank()) +
  theme(axis.text.x = element_blank()) +
  theme(axis.ticks.x = element_blank()) +
  xlab("") +
  scale_fill_brewer(palette = "Set2")

prod_wrap
```
# Compare customer return status by product line and branch
```{r}
prod_grid <- ggplot(qty_sum) +
  geom_bar(aes(ProductLine, Quantity, fill = ProductLine), color = "black", stat = "identity") + 
  facet_grid(CustReturned ~ Branch, switch = "both") +

  # Formatting
  ggtitle("Quantity Sold for Returning vs. Non-Returning Customers") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(panel.grid.major.x = element_blank()) +
  theme(axis.text.x = element_blank()) +
  theme(axis.ticks.x = element_blank()) +
  xlab("") +
  scale_fill_brewer(palette = "Set2")
  
prod_grid
```
# Convert the data frame to a long format
```{r}
library(tidyr)

long_df <- gce_trial %>% pivot_longer(c(CustRating, UnitPrice, Revenue), names_to = "VarNames", values_to = "VarVals")

long_df
```
# Compare income correlations with rating, revenue, and price
```{r}
sctr_wrap <- ggplot(long_df) +
  geom_point(aes(VarVals, GrossIncome, color = Quantity)) +
  facet_wrap(~ VarNames, scales = "free_x") + 
  
  # Formatting
  ggtitle("Correlations with Gross Income") +
  theme(plot.title = element_text(hjust = 0.5)) +
  xlab("") +
  ylab("Gross Income (USD)") +
  scale_color_distiller(palette = "Blues", direction = 1)

sctr_wrap
```