---
title: "Visualizing Data in R"
output: html_notebook
---

# Load the dataset and relevant packages
```{r message = FALSE}




```
# Generate a scatter plot comparing revenue and gross income
```{r}

```
# Generate a line plot of revenue over each day in January
```{r}




```
# Generate a bar chart of each branch's total revenue
```{r}



```
# Generate a histogram showing the distribution of COGS
```{r}

```
# Generate a box plot showing the distribution of COGS
```{r}

```
# Load the ggplot2 package
```{r}

```
# Generate a histogram of revenue
```{r}

```
# Generate violin plots comparing the gross income distribution across each branch
```{r}

```
# Generate stack plots to compare total items sold for each day in the first three months
```{r}





```
# Generate a scatter plot comparing quantity to revenue
```{r}

```
# Generate a jitter plot comparing quantity to revenue by gender
```{r}

```
# Generate a bar chart of mean revenue for each branch for the health and beauty product line
```{r}




```
# Create a data frame for plotting total revenue each day for January and February
```{r}





```
# Generate a line graph of revenue by month
```{r}




```
# Add a title to the plot and format it
```{r}




```
# Modify the axis labels
```{r}





```
# Expand the y-axis upper limit
```{r}



```
# Add more ticks to the x-axis
```{r}



```
# Modify the legend
```{r}



```
# Apply a color palette to the lines and change the legend item labels
```{r}






```
# Change the line types
```{r}



```
# Add an annotation explaining a sharp drop in revenue
```{r}





```
# Save the revenue line plot as a file
```{r}

```
# Generate a bar chart that compares the quantity sold for each product line and branch
```{r}
qty_sum <- gce_trial %>% group_by(ProductLine, Branch, CustReturned) %>% summarize(Quantity = sum(Quantity))

prod_bar <- ggplot(qty_sum) +
  geom_bar(aes(ProductLine, Quantity, fill = Branch), color = "black", position = "dodge", stat = "identity") +
  ggtitle("Quantity Sold for Each Product Line") +
  theme(plot.title = element_text(face = "bold", size = 12, hjust = 0.5)) +
  theme(panel.grid.major.x = element_blank()) +
  theme(axis.text.x = element_text(face = "bold", size = 6)) +
  theme(panel.background = element_rect(fill = "#EFEFFA")) +
  xlab("Product Line") +
  scale_fill_brewer(palette = "Set2") +
  scale_y_continuous(breaks = seq(0, 400, 50)) +
  scale_x_discrete(labels = c("Clothing", "Electronics", "Food and\nbeverages", "Health and\nbeauty", "Home and\nlifestyle", "Sports and\ntravel"))

prod_bar
```
# Compare the distributions of revenue and quantity
```{r}






```
# Compare quantity sold per product line and branch in a facet wrap
```{r}



  
  # Formatting
  ggtitle("Quantity Sold for Each Product Line") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(panel.grid.major.x = element_blank()) +
  theme(axis.text.x = element_blank()) +
  theme(axis.ticks.x = element_blank()) +
  xlab("") +
  scale_fill_brewer(palette = "Set2")

prod_wrap
```
# Compare customer return status by product line and branch
```{r}




  # Formatting
  ggtitle("Quantity Sold for Returning vs. Non-Returning Customers") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(panel.grid.major.x = element_blank()) +
  theme(axis.text.x = element_blank()) +
  theme(axis.ticks.x = element_blank()) +
  xlab("") +
  scale_fill_brewer(palette = "Set2")
  
prod_grid
```
# Convert the data frame to a long format
```{r}





```
# Compare income correlations with rating, revenue, and price
```{r}



  
  # Formatting
  ggtitle("Correlations with Gross Income") +
  theme(plot.title = element_text(hjust = 0.5)) +
  xlab("") +
  ylab("Gross Income (USD)") +
  scale_color_distiller(palette = "Blues", direction = 1)

sctr_wrap
```