---
title: "Modeling Data in R"
output: html_notebook
---

# Load the GCE trial dataset and relevant packages
```{r message = FALSE}




```
# Create a simple linear model of COGS and income
```{r}


```
# Plot the line of best fit for the model
```{r}


```
# Use the simple linear model to make predictions on new data
```{r}




```
# Add the predicted data to the line graph
```{r}



```
# Create a multivariate linear model
```{r}


```
# Sample three values from the dataset at random to use for prediction
```{r}






```
# Use the multivariate linear model to make predictions on sampled data
```{r}



```
# Observe the multivariate predictions on the COGS regression plot
```{r}
cogs_lin_plt + geom_point(data = sample_data, aes(COGS, PredIncome), color = "red", size = 3, shape = "triangle")
```
# Observe the multivariate predictions on the customer ratings regression plot
```{r}
rating_lin_plot <- ggplot(gce_trial, aes(CustRating, GrossIncome)) +
  geom_point() +
  stat_smooth(method = "lm") +
  geom_point(data = sample_data, aes(CustRating, PredIncome), color = "red", size = 3, shape = "triangle")

rating_lin_plot
```
# Create a logistic regression model for customer return status
```{r}


```
# Use the logistic regression model to make predictions on new data
```{r}




```
# Load the time series dataset
```{r}


```
# Create a forecasting model for daily sales
```{r}


```
# Use the forecasting model to predict future sales
```{r}



```
# Add the predicted sales values to the existing data frame
```{r}
apr_week_one <- seq(from = as.POSIXct("2022-04-01"), length.out = proj_days, by = "day")

f_sales <- data.frame(Date = apr_week_one, Sales = f_pred$pred, Status = "Predicted")

gc_daily_sales <- rbind(gc_daily_sales, f_sales)
tail(gc_daily_sales)
```
# Plot the forecasted sales values
```{r}

```
# Select the most relevant features
```{r}


```
# Bin the CustAge feature
```{r}
ml_data <- ml_data %>% mutate(CustAgeBin = case_when(
  CustAge <= 24 & CustAge >= 18 ~ "18–24",
  CustAge <= 34 & CustAge >= 25 ~ "25–34",
  CustAge <= 44 & CustAge >= 35 ~ "35–44",
  CustAge <= 54 & CustAge >= 45 ~ "45–54",
  CustAge <= 64 & CustAge >= 55 ~ "55–64",
  CustAge <= 74 & CustAge >= 65 ~ "65–74",
  CustAge >= 75 ~ "75+"))

ml_data$CustAgeBin <- as.factor(ml_data$CustAgeBin)
ml_data <- ml_data %>% select(-CustAge)
ml_data
```
# Encode the Branch and ProductLine features
```{r}
ml_data <- ml_data %>% mutate(
  BranchCC = case_when(Branch == "Carbon Creek" ~  1L, TRUE ~ 0L),
  BranchGC = case_when(Branch == "Greene City" ~ 1L, TRUE ~ 0L),
  BranchOl = case_when(Branch == "Olinger" ~ 1L, TRUE ~ 0L))

ml_data <- ml_data %>% mutate(
  ProdClth = case_when(ProductLine == "Clothing" ~  1L, TRUE ~ 0L),
  ProdElec = case_when(ProductLine == "Electronics" ~  1L, TRUE ~ 0L),
  ProdFood = case_when(ProductLine == "Food and beverages" ~  1L, TRUE ~ 0L),
  ProdHlth = case_when(ProductLine == "Health and beauty" ~  1L, TRUE ~ 0L),
  ProdHome = case_when(ProductLine == "Home and lifestyle" ~  1L, TRUE ~ 0L),
  ProdSprt = case_when(ProductLine == "Sports and travel" ~  1L, TRUE ~ 0L))

ml_data <- ml_data %>% select(-c("Branch", "ProductLine"))
ml_data
```
# Split the data into training and testing sets
```{r}










```
# Train a decision tree model
```{r}




```
# Use the decision tree to make predictions from test data
```{r}


  
tree_results <- tree_results %>% relocate(Predicted, .before = everything()) %>% relocate(CustReturned, .before = everything())
tree_results
```
# Plot the decision tree
```{r}




```
# Train a random forest model
```{r}




```
# Use the random forest to make predictions from test data
```{r}



  
rf_results <- rf_results %>% relocate(Predicted, .before = everything()) %>% relocate(CustReturned, .before = everything())
tree_results
```
# Identify feature importance
```{r}

```
# Load new transaction data
```{r}


```
# Use the random forest model to predict returning customers from the new data
```{r}
new_data_pred <- predict(rf, new_data)

new_data$Predicted <- new_data_pred

new_data <- new_data %>% relocate(Predicted, .before = everything())
new_data
```