---
title: "Analyzing Data in R"
output: html_notebook
---

# Load the dataset
```{r}
load("../data/gce_trial.rda")
gce_trial
```
# Review the data types of each feature
```{r}
feature_classes <- sapply(gce_trial, class)
feature_classes
```
# Convert the feature to a more appropriate data type
```{r}
gce_trial$CustReturned <- factor(gce_trial$CustReturned)
class(gce_trial$CustReturned)
```
# Identify correlations between the numeric variables
```{r}
library(dplyr)

is_num <- gce_trial %>% sapply(is.numeric) 
num_features <- gce_trial %>% select(which(is_num))
as.data.frame(cor(num_features, use = "complete.obs"))
```
# Generate summary statistics
```{r}
summary(gce_trial)
```
# Generate standard deviation measurements
```{r}
num_features %>% lapply(sd, na.rm = TRUE)
```
# Install and load the moments package
```{r}
install.packages("moments")
library(moments)
```
# Generate skewness measurements
```{r}
num_features %>% lapply(skewness, na.rm = TRUE)
```
# Generate kurtosis measurements
```{r}
num_features %>% lapply(kurtosis, na.rm = TRUE)
```
# Get the top revenue of each branch, not including missing values
```{r}
gce_trial %>% group_by(Branch) %>% summarize(TopRevenue = max(Revenue, na.rm = TRUE))
```
# Identify missing revenue values
```{r}
gce_trial %>% filter(is.na(Revenue)) %>% select(InvoiceID, Revenue)
```
# Get all rows with missing values
```{r}
miss_rows <- gce_trial %>% filter(!complete.cases(.)) %>% select(InvoiceID)
miss_rows <- as.vector(miss_rows$InvoiceID)
miss_cols <- gce_trial %>% select(InvoiceID, function(x) any(is.na(x))) %>% colnames()

missing <- function() {
  gce_trial %>% filter(InvoiceID %in% miss_rows) %>% select(miss_cols)
}

missing()
```
# Fill in the missing gender values
```{r}
gce_trial$CustGender[is.na(gce_trial$CustGender)] <- "Male"
missing()
```
# Fill in the missing quantity values
```{r}
gce_trial$Quantity[is.na(gce_trial$Quantity)] <- c(4L, 3L)
missing()
```
# Identify rows with erroneous quantities
```{r}
gce_trial %>% filter(Quantity < 1) %>% select(InvoiceID, Quantity)
```
# Drop rows with erroneous quantities
```{r}
gce_trial <- gce_trial %>% filter(Quantity > 0)
gce_trial %>% filter(Quantity < 1)
```
# Impute the missing COGS values
```{r}
prct_dif <- gce_trial$COGS / gce_trial$Revenue
mean_dif <- mean(prct_dif, na.rm = TRUE)
calc_vals <- gce_trial %>% filter(is.na(COGS)) %>% select(UnitPrice, Quantity)
imp_cogs <- calc_vals$UnitPrice * calc_vals$Quantity * mean_dif

gce_trial$COGS[is.na(gce_trial$COGS)] <- round(imp_cogs, 2)
missing()
```
# Recalculate revenue and gross income
```{r}
gce_trial$Revenue <- gce_trial$UnitPrice * gce_trial$Quantity
gce_trial$GrossIncome <- gce_trial$Revenue - gce_trial$COGS
missing()
```